\cleardoublepage
\chapternonum{攻读博士学位期间取得的科研成果}

\ifthenelse{\equal{\BlindReview}{true}}
{% For blind review
    \section*{以第一作者身份发表论文}
    \begin{enumerate}
        \item 2018 The 3rd International Conference on Information Communication and Signal Processing of IEEE; EI; 2018。
        \item 《生物医学工程学杂志》; EI; 2023。
    \end{enumerate}

    \section*{以第二作者身份（导师一作）发表论文}
    \begin{enumerate}
        \item Pregnancy Hypertension: An International Journal of Women's Cardiovascular Health ; SCI, IF 2.49; 2019。
        \item Hypertension in Pregnancy; SCI, IF 2.00; 2023。
    \end{enumerate}
}
{% For submission
    \section*{期刊论文}
    \begin{enumerate}
        \item \textbf{Feng Jiang}, Wanlin Chen, Xinzhong Chen, Ying Feng, Jiajun Miao, Cuicui Jiao, Hang Chen. The Research of 
        Photoplethysmography Morphology: Distincting Preeclampsia with Hierarchical Area Ratio[C]. 
        2018 IEEE 3rd International Conference on Signal and Image Processing, 202-206.
        \item Hang Chen, \textbf{Feng Jiang}, Dan Drzymalski, Wanlin Chen, Ying Feng, Jiajun Miao, Cuicui Jiao, Xinzhong Chen. 
        A novel parameter derived from photoplethysmographic pulse wave to distinguish preeclampsia from non-preeclampsia[J]. 
        Pregnancy Hypertension, 2019, 15: 166-170.
        \item Hang Chen, \textbf{Feng Jiang}, Wanlin Chen, Ying Feng, Shali Chen, Jiajun Miao, Cuicui Jiao, Xinzhong Chen. 
        Distinguishing preeclampsia using the falling scaled slope (FSS) --- a novel photoplethysmographic morphological parameter[J]. 
        Hypertension in Pregnancy, 2023, 42(1): 1-10.
        \item \textbf{江锋}, 朱志斌, 张梦鸽, 冯静雯, 徐艺菲, 陈杭. 一种基于新型检测算法的模块化的脉搏波预处理分析系统的设计与实现[J]. 
        生物医学工程学杂志, 2023, 40(3): 529-535.
        %\item Low-power, noninvasive measurement system for wearable ballistocardiography in sitting and standing positions
    \end{enumerate}
    % \includepdf[
    %     pages=-,
    %     scale=0.863,
    %     pagecommand={\pagestyle{fancy}},
    %     % frame, % remove this line if you don't want outer fram of pdf
    % ]{a1.pdf}
    % \includepdf[
    %     pages=-,
    %     scale=0.9,
    %     pagecommand={\pagestyle{fancy}},
    %     % frame, % remove this line if you don't want outer fram of pdf
    % ]{a2.pdf}
}